---
title: "Chandi-A3"
output:
  html_document:
    df_print: paged
---



```{r}
library(tidyverse)
library(mdsr)
library(Lahman)
```

```{r}
db <- dbConnect_scidb("airlines")
flights <- tbl(db, "flights")
carriers <- tbl(db, "carriers")

```


```{sql connection=db}
SELECT carrier, flight,year,month,day,dest,origin
FROM flights
WHERE year=1990 AND month=9 AND day=26 AND dest="LAX" AND origin="JFK";

```


Problem 8
a. List the names of all batters who have at least 300 home runs (HR) and 300 stolen bases 
(SB) in their careers and rank them by career batting average (H/ABH/AB).

```{r}
data("Batting")
data("People")
head(Batting)
```

```{r}
totalHR <- Batting %>% group_by(playerID) %>% summarise(Homeruns = sum(as.numeric(HR), na.rm = TRUE), Stolenbases = sum(as.numeric(SB), na.rm = TRUE),Hits = sum(as.numeric(H),na.rm = TRUE),Atbats = sum(as.numeric(AB),na.rm = TRUE))

df = totalHR[totalHR$Homeruns>=300 & totalHR$Stolenbases>=300,]

df$career_batting_average <- df$Hits/df$Atbats
arrange(df, desc(career_batting_average))
```


b. List the names of all pitchers who have at least 300 wins (W) and 3,000 strikeouts (SO) in 
their careers and rank them by career winning percentage (W/(W+L)W/(W+L)).
```{r}
data("Pitching")
head(Pitching)

```

```{r}
totalP <- Pitching %>% group_by(playerID) %>% summarise(Wins = sum(as.numeric(W), na.rm = TRUE), Strikeouts = sum(as.numeric(SO), na.rm = TRUE),Loses = sum(as.numeric(L),na.rm = TRUE))

df2 = totalP[totalP$Wins >300 & totalP$Strikeouts>3000,]
df2$career_winning_percentage <- df2$Wins/(df2$Wins+df2$Loses)
arrange(df2, desc(career_winning_percentage))
```


c. The attainment of either 500 home runs (HR) or 3,000 hits (H) in a career is considered 
to be among the greatest achievements to which a batter can aspire. These milestones 
are thought to guarantee induction into the Baseball Hall of Fame, and yet several 
players who have attained either milestone have not been inducted into the Hall of 
Fame. Identify them
```{r}
data("HallOfFame")
head(HallOfFame)
```

```{r}
df3 = totalHR[totalHR$Homeruns > 500 & totalHR$Hits > 3000,]
df3
```
```{r}
anti_join(df3, HallOfFame, by='playerID')
```

Problem 10 (Medium): Use the dbConnect_scidb function to connect to the airlines
database to answer the following problem. Find all flights between JFK and SFO in 1994. How 
many were canceled? What percentage of the total number of flights were canceled?

```{sql connection=db}

SELECT count(*)
FROM flights
WHERE year=1994  AND dest="JFK" AND origin="SFO" AND cancelled=0;

```
Problem 11 (Hard): The following open-ended question may require more than one query and 
a thoughtful response. Based on data from 2012 only, and assuming that transportation to the 
airport is not an issue, would you rather fly out of JFK, LaGuardia (LGA), or Newark (EWR)? Why 
or why not? Use the dbConnect_scidb function to connect to the airlines database.
```{r}
head(flights)
```

```{sql connection=db}
SELECT COUNT(*)
FROM flights
WHERE year=2012 AND origin="JFK" OR (origin="LGA" OR origin="EWR") ;

```

