---
title: "Final Case Analysis (EPA)"
output: 
  pdf_document: 
    fig_height: 4
    toc: no
  word_document: 
    fig_height: 4
    toc: yes
  html_document: 
    toc: yes
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```
## Installing pre-required packages
```{r packages}

install.packages("tidyverse")
install.packages("reshape")
library(tidyverse)
library(reshape)
```
## Reading Data Files:
```{r data}
## Loading the data files into Dataframes
dat1 <- read.csv("./data2010.csv",header=TRUE)
dat2 <- read.csv("./data2011.csv",header=TRUE)
dat3 <- read.csv("./data2012.csv",header=TRUE)
dat4 <- read.csv("./data2014.csv",header=TRUE)
dat5 <- read.csv("./data2015.csv",header=TRUE)
dat6 <- read.csv("./data2016.csv",header=TRUE)
dat7 <- read.csv("./data2018.csv",header=TRUE)
dat8 <- read.csv("./data2019.csv",header=TRUE)
dat9 <- read.csv("./data2020.csv",header=TRUE)

## preparing data for the first time period
data1 <- do.call("rbind", list(dat1, dat2, dat3))

## preparing data for the second time period
data2 <- do.call("rbind", list(dat4, dat5, dat6))

## preparing data for the third time period
data3 <- do.call("rbind", list(dat7, dat8, dat9))

```
## Handling Outliers:
```{r Descriptive Analysis}
# Checking for outliers for each of numeric columns
# First Time Period
plot_figures <- function(data){
  ggplot(
  data = melt(data[c("Test.Veh.Displacement..L.", 
                     "X..of.Cylinders.and.Rotors", "X..of.Gears", 
                     "Axle.Ratio")]), 
  aes(x=value, y=variable)) + 
  geom_boxplot(aes(fill=variable, color=variable))

  ggplot(
    data = melt(data[c("N.V.Ratio", "Test.Fuel.Type.Cd", "RND_ADJ_FE", 
                        "FE.Bag.1", "FE.Bag.2", "FE.Bag.3", "Target.Coef.A..lbf.",
                        "Set.Coef.A..lbf.")]), 
    aes(x=value, y=variable)) + 
    geom_boxplot(aes(fill=variable, color=variable))
  
  ggplot(
    data = melt(data[c("THC..g.mi.", "CO..g.mi.", "NOx..g.mi.", "CH4..g.mi.", 
                        "N2O..g.mi.", "Target.Coef.C..lbf.mph..2.", 
                        "Set.Coef.C..lbf.mph..2.")]), 
    aes(x=value, y=variable))+ 
    geom_boxplot(aes(fill=variable, color=variable))
}
plot_figures(data1)
plot_figures(data2)
plot_figures(data3)

```
```{r Data Cleaning NA treatment}
# Dropping missing values for the corresponding columns
data1 <- na.omit(data1)
data2 <- na.omit(data2)
data3 <- na.omit(data3)

```

```{r Missing Values After Omit}
# After droping the missing values, no column names should be displayed
list_na <- colnames(data1)[ apply(data1,2, anyNA) ]
print(list_na)

list_na <- colnames(data2)[ apply(data2,2, anyNA) ]
print(list_na)

list_na <- colnames(data3)[ apply(data3,2, anyNA) ]
print(list_na)

```
## Data Cleaning:
```{r Data Cleaning}
# Replacing the outliers with Upper Bound and Lower Bound
replace_outliers <- function(data){
  data$Test.Veh.Displacement..L.[data$Test.Veh.Displacement..L. > 7.9] <-     
    median(data$Test.Veh.Displacement..L.) 
  data$Rated.Horsepower[data$Rated.Horsepower > 520] <-  
    mean(data$Rated.Horsepower)
  data$X..of.Cylinders.and.Rotors[data$X..of.Cylinders.and.Rotors == 16] <-  
    mean(data$X..of.Cylinders.and.Rotors)
  data$Equivalent.Test.Weight..lbs..[data$Equivalent.Test.Weight..lbs.. > 6000] <- 
    6000
  data$Axle.Ratio[data$Axle.Ratio < 2.4] <- 2.4
  data$Axle.Ratio[data$Axle.Ratio > 5] <- 5
  data$N.V.Ratio[data$N.V.Ratio > 46] <- 46
  data$N.V.Ratio[data$N.V.Ratio < 20] <- 20
  data$Test.Fuel.Type.Cd[data$Test.Fuel.Type.Cd > 61] <- 61
  data$THC..g.mi.[data$THC..g.mi. > 0.2] <- 0.2
  data$CO..g.mi.[data$CO..g.mi. > 2] <- 2
  data$CO..g.mi.[data$CO..g.mi. > 1] <- 1
  data$CO2..g.mi.[data$CO2..g.mi. > 601] <- 601
  data$NOx..g.mi.[data$NOx..g.mi. > 0.03] <- 0.03
  data$CH4..g.mi.[data$CH4..g.mi. > 0.01] <- 0.01
  data$N2O..g.mi.[data$N2O..g.mi. < 0.00992] <- 0.00992
  data$FE.Bag.1[data$FE.Bag.1 < 18.9] <- 18.9
  data$FE.Bag.1[data$FE.Bag.1 > 24] <- 24
  data$FE.Bag.2[data$FE.Bag.2 < 14.9] <- 14.9
  data$FE.Bag.2[data$FE.Bag.2 > 40] <- 40
  data$FE.Bag.3[data$FE.Bag.3 < 14.9] <- 14.9
  data$FE.Bag.3[data$FE.Bag.3 > 40] <- 40
  data$Target.Coef.A..lbf.[data$Target.Coef.A..lbf. > 60.5] <- 60.5
  data$Target.Coef.A..lbf.[data$Target.Coef.A..lbf. < 15.31] <- 15.31
  data$Target.Coef.B..lbf.mph.[data$Target.Coef.B..lbf.mph. < -0.479] <- -0.479
  data$Target.Coef.B..lbf.mph.[data$Target.Coef.B..lbf.mph. > 1.004] <- 1.004
  data$Target.Coef.C..lbf.mph..2.[data$Target.Coef.C..lbf.mph..2. > 0.036] <- 
    0.036
  data$Target.Coef.C..lbf.mph..2.[data$Target.Coef.C..lbf.mph..2. < 0.01] <- 
    0.009997
  data$Set.Coef.A..lbf.[data$Set.Coef.A..lbf. > 36.18] <- 36.18
  data$Set.Coef.A..lbf.[data$Set.Coef.A..lbf. < -8] <- -8
  data$Set.Coef.B..lbf.mph.[data$Set.Coef.B..lbf.mph. > 0.78] <- 0.78
  data$Set.Coef.B..lbf.mph.[data$Set.Coef.B..lbf.mph. < -0.5] <- -0.5
  data$Set.Coef.C..lbf.mph..2.[data$Set.Coef.C..lbf.mph..2. > 0.041] <- 0.041
  data$Set.Coef.C..lbf.mph..2.[data$Set.Coef.C..lbf.mph..2. < 0.004] <- 0.004
}
replace_outliers(data1)
replace_outliers(data2)
replace_outliers(data3)
```
## Dimension Reduction:
```{r PCA}
# Using Principle-Component Analysis to get the 8 variable which explain the 
# most variance

# First Time Period
data1_pca <- prcomp(data1[, c(6,8,12,16:18,21,24:29,31:39)], rank.=8,center =
                      TRUE,  scale. = TRUE)

new_data1 <- cbind(data1_pca$x, data1[30])

# Second Time Period
data2_pca <- prcomp(data2[, c(6,8,12,16:18,21,24:29,31:39)], rank.=8,center = 
 TRUE,scale. = TRUE)

new_data2 <- cbind(data2_pca$x, data2[30])

# Third Time Period
data3_pca <- prcomp(data3[, c(6,8,12,16:18,21,24:29,31:39)], rank.=8,center = 
  TRUE,scale. = TRUE)

new_data3 <- cbind(data3_pca$x, data3[30])

```

## Grouping of Similar Vehicles:
```{r Grouping}
# Create 8 subgroups for each of the time periods based on Horse Power and 
# First Time Period
data1_group1 <- subset(data1, (data1$Rated.Horsepower < 260 & data1$RND_ADJ_FE  
                               < 27 & data1$THC..g.mi. < 0.02 ))
data1_group2 <- subset(data1, (data1$Rated.Horsepower < 260 & data1$RND_ADJ_FE  
                               < 27 & 
data1$THC..g.mi. > 0.02 ))
data1_group3 <- subset(data1, (data1$Rated.Horsepower < 260 & data1$RND_ADJ_FE  
                               > 27 & 
data1$THC..g.mi. < 0.02 ))
data1_group4 <- subset(data1, (data1$Rated.Horsepower < 260 & data1$RND_ADJ_FE  
                               > 27 & 
data1$THC..g.mi. > 0.02 ))
data1_group5 <- subset(data1, (data1$Rated.Horsepower > 260 & data1$RND_ADJ_FE  
                               < 27 & 
data1$THC..g.mi. < 0.02 ))
data1_group6 <- subset(data1, (data1$Rated.Horsepower > 260 & data1$RND_ADJ_FE  
                               < 27 & 
data1$THC..g.mi. > 0.02 ))
data1_group7 <- subset(data1, (data1$Rated.Horsepower > 260 & data1$RND_ADJ_FE  
                               > 27 & 
data1$THC..g.mi. < 0.02 ))
data1_group8 <- subset(data1, (data1$Rated.Horsepower > 260 & data1$RND_ADJ_FE  
                               > 27 & 
data1$THC..g.mi. > 0.02 ))


# Second Time Period
data2_group1 <- subset(data2, (data2$Rated.Horsepower < 260 & data2$RND_ADJ_FE  
                               < 27 & 
data2$THC..g.mi. < 0.02 ))
data2_group2 <- subset(data2, (data2$Rated.Horsepower < 260 & data2$RND_ADJ_FE  
                               < 27 & 
data2$THC..g.mi. > 0.02 ))
data2_group3 <- subset(data2, (data2$Rated.Horsepower < 260 & data2$RND_ADJ_FE  
                               > 27 & 
data2$THC..g.mi. < 0.02 ))
data2_group4 <- subset(data2, (data2$Rated.Horsepower < 260 & data2$RND_ADJ_FE  
                               > 27 & 
data2$THC..g.mi. > 0.02 ))
data2_group5 <- subset(data2, (data2$Rated.Horsepower > 260 & data2$RND_ADJ_FE  
                               < 27 & 
data2$THC..g.mi. < 0.02 ))
data2_group6 <- subset(data2, (data2$Rated.Horsepower > 260 & data2$RND_ADJ_FE  
                               < 27 & 
data2$THC..g.mi. > 0.02 ))
data2_group7 <- subset(data2, (data2$Rated.Horsepower > 260 & data2$RND_ADJ_FE  
                               > 27 & 
data2$THC..g.mi. < 0.02 ))
data2_group8 <- subset(data2, (data2$Rated.Horsepower > 260 & data2$RND_ADJ_FE  
                               > 27 & 
data2$THC..g.mi. > 0.02 ))


# Third Time Period
data3_group1 <- subset(data3, (data3$Rated.Horsepower < 260 & data3$RND_ADJ_FE  
                               < 27 & data3$THC..g.mi. < 0.02 ))
data3_group2 <- subset(data3, (data3$Rated.Horsepower < 260 & data3$RND_ADJ_FE  
                               < 27 & data3$THC..g.mi. > 0.02 ))
data3_group3 <- subset(data3, (data3$Rated.Horsepower < 260 & data3$RND_ADJ_FE  
                               > 27 & data3$THC..g.mi. < 0.02 ))
data3_group4 <- subset(data3, (data3$Rated.Horsepower < 260 & data3$RND_ADJ_FE  
                               > 27 & data3$THC..g.mi. > 0.02 ))
data3_group5 <- subset(data3, (data3$Rated.Horsepower > 260 & data3$RND_ADJ_FE  
                               < 27 & data3$THC..g.mi. < 0.02 ))
data3_group6 <- subset(data3, (data3$Rated.Horsepower > 260 & data3$RND_ADJ_FE  
                               < 27 & data3$THC..g.mi. > 0.02 ))
data3_group7 <- subset(data3, (data3$Rated.Horsepower > 260 & data3$RND_ADJ_FE  
                               > 27 & data3$THC..g.mi. < 0.02 ))
data3_group8 <- subset(data3, (data3$Rated.Horsepower > 260 & data3$RND_ADJ_FE  
                               > 27 & data3$THC..g.mi. > 0.02 ))

```
## Compare the Groups:
```{r Compare}
# Comparing the groups for the three time periods, to check if any vehicles
# has moved from one group to other
a<- levels(data1_group1$Veh.Mfr.Code)
b<-levels(data2_group1$Veh.Mfr.Code)
c<-levels(data3_group1$Veh.Mfr.Code)

d<- levels(data1_group2$Veh.Mfr.Code)
e<- levels(data2_group2$Veh.Mfr.Code)
f<- levels(data3_group2$Veh.Mfr.Code)

g<- levels(data1_group3$Veh.Mfr.Code)
h<- levels(data2_group3$Veh.Mfr.Code)
i<- levels(data3_group3$Veh.Mfr.Code)


j<- levels(data1_group4$Veh.Mfr.Code)
k<- levels(data2_group4$Veh.Mfr.Code)
l<- levels(data3_group4$Veh.Mfr.Code)

m<- levels(data1_group5$Veh.Mfr.Code)
n<- levels(data2_group5$Veh.Mfr.Code)
o<- levels(data3_group5$Veh.Mfr.Code)

p<- levels(data1_group6$Veh.Mfr.Code)
q<- levels(data2_group6$Veh.Mfr.Code)
r<- levels(data3_group6$Veh.Mfr.Code)

s<- levels(data1_group7$Veh.Mfr.Code)
t<- levels(data2_group7$Veh.Mfr.Code)
u<- levels(data3_group7$Veh.Mfr.Code)

v<- levels(data1_group8$Veh.Mfr.Code)
w<- levels(data2_group8$Veh.Mfr.Code)
x<- levels(data3_group8$Veh.Mfr.Code)

Reduce(intersect, list(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w,x))

```
## Inference from Grouping and Comparison of Groups:
```

Since we have common manufacturing code across time periods and across data 
groups we can say that many vehicles have jumped from one group to other over 
the time period of study due to increased fuel emission over the time period, 
and hence those values are not within the boundaries of the previous groups they
belonged to.
```
## Predictive Modeling:
```{r Splitting the dataset into training and test sets}
# Splitting the dataset of the three time periods into the corresponding 
# training and test sets

library(heatmaply)
library(Metrics)
# First Time Period
smp_size <- floor(0.75* nrow(new_data1))
train_ind <- seq(1,smp_size)
test_ind <- seq(smp_size+1,nrow(new_data1))
data1_train <- new_data1[train_ind,]
data1_test <- new_data1[test_ind,]

smp_size <- floor(0.75* nrow(new_data2))
train_ind <- seq(1,smp_size)
test_ind <- seq(smp_size+1,nrow(new_data2))
data2_train <- new_data2[train_ind,]
data2_test <- new_data2[test_ind,]

smp_size <- floor(0.75* nrow(new_data3))
train_ind <- seq(1,smp_size)
test_ind <- seq(smp_size+1,nrow(new_data3))
data3_train <- new_data3[train_ind,]
data3_test <- new_data3[test_ind,]
```
## Linear Regression Model:
```{r Linear Regression Model}
# Linear regression model
build_linear_model <- function(train, test) {
  attach(train)
  lm1 <- lm(RND_ADJ_FE~PC1+PC2+PC3+PC4+PC5+PC6+PC7+PC8, data=train)
  summary(lm1)
  pred1 <- predict(lm1,test)
  
  results1 <- data.frame(pred1 = pred1, original=test$RND_ADJ_FE)
  
  print(paste("RSE: ", rse(results1$pred1,results1$original)))
  print(paste("RMSE: ", rmse(results1$pred1,results1$original)))
  print(paste("MSLE: ", msle(results1$pred1,results1$original)))
  print(paste("SSE: ", sse(results1$pred1,results1$original)))
  print(paste("MAE: ", mae(results1$pred1,results1$original)))
  print(paste("MAPE: ", mape(results1$pred1,results1$original)))
  qplot(lm1$fitted.values,lm1$residuals, main="Fitted Values vs. Residuals",
       xlab = "Fitted Values", ylab="Residuals",geom=c("point", "line"))
  qplot(test$RND_ADJ_FE, pred1, ylab="predictions", geom=c("point", "line"))
}

# Linear regression model on the first time period
build_linear_model(data1_train, data1_test)
# Linear regression model on the second time period
build_linear_model(data2_train, data2_test)
# Linear regression model on the third time period
build_linear_model(data3_train, data3_test)

```
## Non Linear Regression Model of Degree 2:
```{r Non Linear Regression Model of Degree 2}
# Non-Linear regression model; Degree = 2 
build_nonlinear_model <- function(train, test, degree){
  n_lm <- lm(RND_ADJ_FE~poly(PC1+PC2+PC3+PC4+PC5+PC6+PC7+PC8, degree, raw=TRUE), 
  data=train)
  summary(n_lm)
  pred1 <- predict(n_lm,test)
  
  results1 <- data.frame(pred1 = pred1, original=test$RND_ADJ_FE)
  print(paste("RSE: ", rse(results1$pred1,results1$original)))
  print(paste("RMSE: ", rmse(results1$pred1,results1$original)))
  print(paste("MSLE: ", msle(results1$pred1,results1$original)))
  print(paste("SSE: ", sse(results1$pred1,results1$original)))
  print(paste("MAE: ", mae(results1$pred1,results1$original)))
  print(paste("MAPE: ", mape(results1$pred1,results1$original)))
  qplot(n_lm$fitted.values,n_lm$residuals, main="Fitted Values vs. Residuals",
       xlab = "Fitted Values", ylab="Residuals",geom=c("point", "line"))
  qplot(test$RND_ADJ_FE, pred1, ylab="predictions", geom=c("point", "line"))
}
# Non-Linear regression model (Degree=2) on the First Time Period
build_nonlinear_model(data1_train, data1_test, 2)
# Non-Linear regression model (Degree=2) on the Second Time Period
build_nonlinear_model(data2_train, data2_test, 2)
# Non-Linear regression model (Degree=2) on the Third Time Period
build_nonlinear_model(data3_train, data3_test, 2)

```
## Non Linear Regression Model of Degree 3:
```{r Non Linear Regression Model of Degree 3}
# Non-Linear regression model (Degree=3) on the First Time Period
build_nonlinear_model(data1_train, data1_test, 3)
# Non-Linear regression model (Degree=3) on the Second Time Period
build_nonlinear_model(data2_train, data2_test, 3)
# Non-Linear regression model (Degree=3) on the Third Time Period
build_nonlinear_model(data3_train, data3_test, 3)
```

## Conclusion:
In conclusion, we see that due to wear and tear in the vehicles, certain 
vehicles became more polluting over the period of study.
