---
title: "IIAG"
output:
  html_document:
    df_print: paged
---

Libraries
```{r}
library(stargazer)
library(moments)

```

```{r}
df <- read.csv("IIAG.csv")
#variables in use
df$AbsForcLab <- suppressWarnings(as.numeric(df$AbsForcLab))
df$AbsGovViolenceCivACLED <- suppressWarnings(as.numeric(df$AbsGovViolenceCivACLED))
df$EffFightHumTrafUSDS <- suppressWarnings(as.numeric(df$EffFightHumTrafUSDS ))
df$AbsCrim <- suppressWarnings(as.numeric(df$AbsCrim))

#Removing missing variables
na.omit(df)
```

#descriptive statistics
```{r, results='asis', echo = FALSE , eval=TRUE, warning=FALSE, message=FALSE}
stargazer(df[,c("AbsForcLab","AbsGovViolenceCivACLED","EffFightHumTrafUSDS","AbsCrim")], header=FALSE, type='html', title="Descriptive Statistics",digits=1)

```
#correlation matrix
```{r, results='asis', echo = FALSE , eval=TRUE, warning=FALSE, message=FALSE}
stargazer(cor(df[,c("AbsForcLab","AbsGovViolenceCivACLED","EffFightHumTrafUSDS","AbsCrim")],use="complete.obs") ,header=FALSE, type='html', title="Correlation Matrix",digits=1)

```
The further away the correlation coefficient is from zero, the stronger the relationship between the two variables.

#Are the distributions of any component measures highly skewed
```{r}

skewness(df$AbsForcLab,na.rm = TRUE)
skewness(df$AbsGovViolenceCivACLED, na.rm = TRUE)
skewness(df$EffFightHumTrafUSDS, na.rm = TRUE)
skewness(df$AbsCrim,na.rm = TRUE)

```
If the coefficient of skewness is close to 0 i.e. between -0.5 to +0.5, then the data is said to be symmetric.only the "EffFightHumTrafUSDS" variable in our case is symmetric and does not require scaling.

#perform log transformation on the other three variables
```{r}
df$AbsForcLab_log <- log(df$AbsForcLab)
df$AbsGovViolenceCivACLED_log <- log(df$AbsGovViolenceCivACLED)
df$EffFightHumTrafUSDS_log <- log(df$EffFightHumTrafUSDS)
df$AbsCrim_log <- log(df$AbsCrim)

```
#transform the measures onto a common scale using z-scores
```{r}
#standardize AbsForcLab
df$AbsForcLab <- (df$AbsForcLab- mean(df$AbsForcLab)) / sd(df$AbsForcLab)
#standardize AbsGovViolenceCivACLED
df$AbsGovViolenceCivACLED<-(df$AbsGovViolenceCivACLED-mean(df$AbsGovViolenceCivACLED))/sd(df$AbsGovViolenceCivACLED)
#standardize df$EffFightHumTrafUSDS
df$EffFightHumTrafUSDS <- (df$EffFightHumTrafUSDS- mean(df$EffFightHumTrafUSDS)) / sd(df$EffFightHumTrafUSDS)
#standardize AbsForcLab
df$AbsCrim <- (df$AbsCrim - mean(df$AbsCrim)) / sd(df$AbsCrim)
```

#Do you take an unweighted arithmetic mean of the rescaled indicators
```{r, results='asis', echo = FALSE , eval=TRUE, warning=FALSE, message=FALSE}
stargazer(df[,c("AbsForcLab_log","AbsGovViolenceCivACLED_log","EffFightHumTrafUSDS_log","AbsCrim_log")], header=FALSE, type='html', title="Descriptive Statistics",digits=1,  summary.stat=c("n","mean"))

```
The geometric mean introduces Nas as shown below
```{r}
apply(df[,c("AbsForcLab_log","AbsGovViolenceCivACLED_log","EffFightHumTrafUSDS_log","AbsCrim_log")], 2, function(x) exp(mean(log(x))))


```

#identify about three measures not in the index that you would expect to be correlated with the index
```{r, results='asis', echo = FALSE , eval=TRUE, warning=FALSE, message=FALSE}
#the three other measures
df$AbsViolEvStateConfACLED <- suppressWarnings(as.numeric(df$AbsViolEvStateConfACLED))
df$AbsNonStateConfUCDP <- suppressWarnings(as.numeric(df$AbsNonStateConfUCDP))
df$AbsViolEvNonStateConfACLED <- suppressWarnings(as.numeric(df$AbsViolEvNonStateConfACLED))



stargazer(cor(df[,c("AbsViolEvStateConfACLED","AbsNonStateConfUCDP","AbsViolEvNonStateConfACLED")],use="complete.obs") ,header=FALSE, type="html", title="Correlation Matrix",digits=1)

```
The further away the correlation coefficient is from zero, the stronger the relationship between the two variables.



