---
title: "R Notebook"
output: html_notebook
---


View Layer
```{r}
namespace ViewLayer
{
  public partial class FrmDemo : Form{
    public FrmDemo ()
    InitializeComponent ();
    BusinessLayer. Customer Info info = BusinessLayer. CustomerInfo. GetCustomer (1);
}
  private void GetCustomer_Click(object sender, EventArgs e)
  NormalBusinessLayer.CustomerInfo info = NormalBusinessLayer.CustomerInfo.GetCustomer(1);
  MessageBox. Show("Get customer done. . . ");
}

```
This layer of the code is the View part that is to be displayed to the end user of the application, in other words the front end of the application


Business Layer
```{r}

namespace NormalBusinessLayer
{
  public class CustomerInfo
  {
    public static CustomerInfo GetCustomer (int id)
    {
    Customer cust = new Customer();
    IDataReader dr = cust.GetCustomer(id);
    return null;
    }
  }

}

```


This layer of the code provides the business logic for the front end of the application . This layer does all the complex activity and communicates with the datalyer.


Normal Layer
```{r}
namespace NormalDataLayer{
  public class Customer{
    public IDataReader GetCustomer (int id){
      #code to call database and get data
      return null;
    }
  }
}

```

This layer of code communicates with the DataBase or DataStructure where the data is stored and brings that data out of it.



```{r}
using System;
using System.Collections.Generic;
using System.Ling;
using System.Text;

using System.Threading.Tasks;
namespace LinqFirstAndFirstOrDefault{
  class Employee{
    public int Id { get; set; }
    public string Name { get; set; }
    public string City { get; set; }
    
  }
    
  public class Program{
      static void Main(string[] args){
        IList <Employee> employeeList = new List<Employee>(){
        new Employee() { Id = 10, Name = "Chris", city = "London" },
        new Employee() { Id=11, Name="Robert", City="London"},
        new Employee() { Id=12, Name="Mahesh", City="India"},
        new Employee() { Id=13, Name="Peter", City="US"},
        new Employee() { Id=14, Name="Chris", City="US"}
        };
    
    #First example
    var result1 = employeeList.First();
    #It will return the first element like Id = 10, Name = "Chris", city = "London"
    
    var result2 = employeeList. First(e => e.Id == 12) ;
    #It will return the first element like Id=12, Name="Mahesh", City="India";
    
    var result3 = employeeList. First(e => e.Name == "Chris");
    #Two records available for Name=Chris but it will return the first like Id = 10,Name = "chris", City = "London";
    
    var result4 = employeeList. First(e => e.Id == 16);
    #No element for Id=16 so, It throws an exception that Sequence contains more than  one matching elemen
    
    #FirstorDefault example
    
    var result5 = employeeList.FirstorDefault();
    #It will return the first element like Id = 10, Name = "Chris", city = "London";
    
    var result6 = employeeList.FirstOrDefault(e => e.Id == 12);
    #It will return the first element like Id=12, Name="Mahesh", City="India";
    
    var result7 = employeeList. FirstorDefault(e => e.Name == "Chris");
    #Two records available for Name=Chris but it will return the first like Id = 10,Name = "Chris", City = "London";

    var results = employeeList. FirstorDefault(e => e.Id == 16);
    #No element for Id=16 so, It return null for default;

    Console. ReadLine() ;

    }
  }
}
```

```{r}

using System;
using System.Linq;
using System. Collections.Generic;

class Demo{
  
  static public void Main()
 {
     IList<int> List1 = new List<int>( ) {8, 11, 22, 37, 58, 97 };
     IList<string> List2 = new List<string>() {"Apple", "Orange", "Banana" };
    
     IList<string> List3 = new List<string>() { null ,"one", "two", "three" };
     IList<string> List4 = new List<string>();
    
     Console. WriteLine("ist element in List 1 is {0}", List1. FirstorDefault());
     Console. WriteLine("ist even element in List 1 is {o}",
     List1. FirstOrDefault(i=> i % 2==0) );
    
     Console. WriteLine("ist element in List 2 is {}", List2. FirstorDefault( ));
     Console. WriteLine("ist element in List 3 is {0]", List3. FirstorDefault( ));
     Console. WriteLine("ist element in List 4 is {}", List4. FirstorDefault());
}


```

```{r}
using System;
using System.Linq;
using System. Collections . Generic;
class Program
{
static public void Main(){
  int[] seq1 = {122, 33, 55, 77, 243, 65};
  var result1 = seq1. FirstOrDefault(sequence => sequence < 77);
  Console. WriteLine( "The value is fo} ", resulti);


 int[ ] seq2= {};
 var result2 = seq2. FirstOrDefault( );
  Console. WriteLine("Our default value is {o} ", result2);
}
 }
```